### 2021-07-19 doc/thesis/chapters/system-design-process.tex
notes
structure sections
chapter begin

>>>>

The process of system design is a central topic in the development of any product.
This chapter describes general techniques for system design.
However, they can also be directly applied to FPGA design.
Additionally, tools that are specifically used in FPGA design are introduced.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{General}

The research for this chapter is mainly based on \cite{BahillA.Terry2017TDiS}.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The SIMILAR Process}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design for Reuse}
%see pg. 51

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Problem Statement}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Concept Exploration}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation and Verification}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Design Targeting FPGAs}
The research for this chapter is mainly based on \cite{GesslerRalf2014EES}.
%https://link-springer-com.fhooe.idm.oclc.org/content/pdf/10.1007%2F978-3-319-26408-0.pdf
%chapter 3

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{V-Modell}

%applies to general software development, but can directly be mapped to FPGA development.

%Abbildung 3.5 in
%https://link-springer-com.fhooe.idm.oclc.org/content/pdf/10.1007%2F978-3-8348-2080-8.pdf

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{High-Level Synthesis}
%\cplusplus\\
%SystemC (deprecated for synthesis by Xilinx)\\

A comprehensive list of HLS tools can be found in Section 3.3 of
%https://link-springer-com.fhooe.idm.oclc.org/content/pdf/10.1007%2F978-3-319-26408-0.pdf

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Implementation with Tool Support}
%https://link-springer-com.fhooe.idm.oclc.org/content/pdf/10.1007%2F978-3-8348-2080-8.pdf

%Matlab Simulink System Generator\\
%Matlab Simulink HDL Coder\\

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Direct Implementation}

%direct, or 'manual' implementation\\
%VHDL/Verilog\\
